Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-27 paper/EDA.qmd
EDA paper setup

---
title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
subtitle: "Based on Data Collected From the University of Queensland"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly. This study discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts. Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents. Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact. These findings highlight critical areas for how organizations can improve their security and protect their data."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}

format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

library(tidyverse)
library(readxl)
library(here)

breach_data <- read.csv(here("data/analysis_data/breach_data.csv"))
```

>>>>

---
title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
---

@@

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)

clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
```

library(performance)
library(knitr)
library(ggplot2)

# Compute summary statistics for all numeric variables
summary_stats <- clean_data %>%
  summarise(
    Mean_GameBefore = mean(game_before, na.rm = TRUE),
    Median_GameBefore = median(game_before, na.rm = TRUE),
    SD_GameBefore = sd(game_before, na.rm = TRUE),
    IQR_GameBefore = IQR(game_before, na.rm = TRUE),

    Mean_GameAfter = mean(game_after, na.rm = TRUE),
    Median_GameAfter = median(game_after, na.rm = TRUE),
    SD_GameAfter = sd(game_after, na.rm = TRUE),
    IQR_GameAfter = IQR(game_after, na.rm = TRUE)
  )

# Display summary statistics in a table
knitr::kable(summary_stats, caption = "Summary Statistics for Memory Game Scores")

```
